% This is biblio.tex
 
%% Enter your formatted bibliography information into this file.
%% Use a format appropriate to a journal in your field.

%% DO NOT TOUCH THIS LINE UNLESS YOU REALLY KNOW WHAT YOU'RE DOING
\begin{thebibliography}{99}

%% Enter your formatted \bibitem{key} info here.

\bibitem{pickersgill} Pickersgill M. From psyche to soma? Changing accounts of antisocial personality disorders in the American Journal of Psychiatry {\it History of Psychiatry}. 2010. 21(3):294-311.

\bibitem{ferguson} Ferguson C. Genetic contributions to antisocial personality and behavior: a meta-analytic review from an evolutionary perspective {\it Journal of Social Psychology}. 2010. 150(2):160-180.

\bibitem{meyers} Meyers CA, Berman SA, Scheibel RS, Hayman A. Case report: acquired antisocial personality disorder associated with unilateral left orbital frontal lobe damage. {\it J Psychiatry Neurosci}. 1992 Sep;17(3):121-5.

\bibitem{psychcentral} Black D. Treatment for Antisocial Personality Disorder. \it{Psych Central}. 2006. Available at \url{http://psychcentral.com/lib/2006/treatment-for-antisocial-personality-disorder/2/} (April 22, 2011).


\bibitem{davidson} Davidson KM, Tyrer P, Tata P, Cooke D, Gumley A, Ford I, Walker A, Bezlyak V, Seivewright H, Robertson H, Crawford MJ. Cognitive behaviour therapy for violent men with antisocial personality disorder in the community: an exploratory randomized controlled trial. {\it Psychol Med.} 2009 Apr;39(4):569-77. Epub 2008 Jul 30.

\bibitem{freeman} Freeman W. Psychosurgery. {\it Journal of the National Medical Association}. July 1950. pp206-209.

\bibitem{black} Black DW. Antisocial personality disorder in incarcerated offenders: Psychiatric comorbidity and quality of life. {\it Annals of Clinical Psychiatry}. 2010;22(2):113-120.



%% YOU SHOULD NOT HAVE TO CHANGE THIS LINE
\end{thebibliography}
