% This is biblio.tex
 
%% Enter your formatted bibliography information into this file.
%% Use a format appropriate to a journal in your field.

%% DO NOT TOUCH THIS LINE UNLESS YOU REALLY KNOW WHAT YOU'RE DOING
\begin{thebibliography}{99}

%% Enter your formatted \bibitem{key} info here.

\bibitem{medscape} Avolio L. Genital Anomalies. {\it Medscape Reference}. 24 Oct 2008. Available at \url{http://emedicine.medscape.com/article/1016681-overview} (April 2, 2011).

\bibitem{biblios20:13} {\it The ESV® Bible (The Holy Bible, English Standard Version®)}. ESV® Text Edition: 2007. Available at \url{http://bible.cc/leviticus/20-13.htm} (April 3, 2011).

\bibitem{chase} Chase C. Hermaphrodites with attitude: Mapping the emergence of intersex political activism {\it GLQ}. 1998; 35(2):65-83.

\bibitem{fausto} Fausto-Sterling A.  The five sexes: why male and female are not enough. {\it The Sciences} March/April 1993, p20-24;

\bibitem{franklin} Franklin S. Sex. {\it Dolly mixtures: the remaking of genealogy}. 2007. Duke University Press.

\bibitem{levay} Levay S.  A difference in hypothalamic structure between heterosexual and homosexual men. {\it Science} 30 Aug 1991; 254(5032):630.

\bibitem{libidomag} Lynnell SL. A Girl Named Steve. {\it Libido: The Journal of Sex and Sexuality}. (No Publication Date). Available at \url{http://www.libidomag.com/nakedbrunch/archive/girlsteve.html} (April 2, 2011).

\bibitem{time} Melnick M. Passing as Black: How Biracial Americans Choose Identity. {\it TIME}. 16 Dec 2010. Available at \url{http://healthland.time.com/2010/12/16/passing-as-black-how-biracial-americans-choose-identity/} (April 5, 2011).

\bibitem{webster} Merriam-Webster Dictionary. Sex. {\it Merriam-Webster Dictionary}. No date. Available at \url{http://www.merriam-webster.com/dictionary/sex} (23 Mar 2011).

\bibitem{savic} Savic I, Garcia-Falgueras A, Swaab DF.  Sexual differentiation of the human brain in relation to gender identity and sexual orientation. {\it Progress in Brain Research}. 2010;186:41-62.

\bibitem{census} US Census Bureau, Population Division. Racial and Ethnic Classifications Used in Census 2000 and Beyond. {\it US Census Bureau}. (No date). Available at \url{http://www.census.gov/population/www/socdemo/race/racefactcb.html} (April 2, 2011).

\bibitem{pubmed-hypo} Vorvick L.  Hypospadius. {\it Pubmed Health}. 3 Sept 2010. Available at \url{http://www.ncbi.nlm.nih.gov/pubmedhealth/PMH0002265/}


%% YOU SHOULD NOT HAVE TO CHANGE THIS LINE
\end{thebibliography}
