% This is biblio.tex
 
%% Enter your formatted bibliography information into this file.
%% Use a format appropriate to a journal in your field.

%% DO NOT TOUCH THIS LINE UNLESS YOU REALLY KNOW WHAT YOU'RE DOING
\begin{thebibliography}{99}

%% Enter your formatted \bibitem{key} info here.

\bibitem{mayo_ana} Anabolic Steroid (Oral Route, Parenteral Route). {\it Mayo Clinic}. 1 Nov 2010. Available at \url{http://www.mayoclinic.com/health/drug-information/DR602077}

\bibitem{carey} Carey B.  Brain Enhancement Is Wrong, Right? {\it The New York Times}. 9 March 2008. Available at \url{http://www.nytimes.com/2008/03/09/weekinreview/09carey.html}

\bibitem{delaney} Delaney T. {\it The Sociality of Sports.}. (April 2, 2011).

\bibitem{checkana} Franklin S. Anabolic Steroids Control Act Of 1990 . {\it Anabolic Steroids}. No date. Available at \url{http://www.checkanabolicsteroids.com/buynsale/anabolic-steroids-control-act-of-1990.html}

\bibitem{grogan} Gorgan J and Long C.  The Problem with Genetic Engineering. {\it Vegiheal Voice} December 2000. Vol 1, no. 3.

\bibitem{massey} Massey A. Working on the food chain. {\it Gastronomica: The Journal of Food and Culture} 
\bibitem{mehta} Mehta, P. H., and Josephs, R. A. (in press). Testosterone. In R. Baumeister and K. D. Vohs (Eds.),{\it Encyclopedia of Social Psychology}. Thousand Oaks, CA: Sage.

\bibitem{mw} Merriam-Webster Dictionary. Anabolic steroid. {\it Merriam-Webster Dictionary}. No date.(23 April 2011).
\bibitem{nida} National Institute on Drug Abuse. NIDA InfoFacts: Steroids (Anabolic-Androgenic). {\it NIDA - The Science of Drug Abuse and Addiction}. Sept 2009. Available at \url{http://www.drugabuse.gov/infofacts/steroids.html} (May 2, 2011).

\bibitem{meso} Roberts B. History of Anabolic Steroids. The History and Present Status of The Drug Development of Anabolic / Androgenic Steroids {\it MesoRx}. Available at \url{http://www.mesomorphosis.com/articles/pharmacology/history-of-anabolic-steroids.htm#The\%20Discovery\%20of\%20Testosterone} (May 3, 2011).

\bibitem{stehlin} Stehlin D. For athletes and dealers, black market steroids are risky business {\it FDA Consumer}. Sept 1987. Available at \url{http://findarticles.com/p/articles/mi_m1370/is_v21/ai_5242330/} (May 5, 2011).

\bibitem{tricker} Tricker R, O'Neill MR, Cook D. The incidence of anabolic steroid use among competitive bodybuilders. {\it Journal of Drug Education}. 1989. Vol 19(4).pp313-325.
\bibitem{yesalis} Yesalis CE, Courson SP and Wright J.  History of anabolic steroid use in sport and exercise.  {\it Anabolic steroids in sport and exercise} Ed: Yesalis, CE. 2nd ed Champaign, IL:Human Kinetics. 51-71.
%% YOU SHOULD NOT HAVE TO CHANGE THIS LINE
\end{thebibliography}
